Invariant Generation using ACDL

### 2016-08-06 invariant.tex
gamma completeness and spurious check algorithm

>>>>

\begin{algorithm2e}[t]
\DontPrintSemicolon
\SetKwFunction{decide}{Decide}
\SetKwFunction{deduce}{deduce}
\SetKwFunction{backtrack}{backtrack}
\SetKwFunction{print}{print}
\SetKwFunction{return}{return}
\SetKwFunction{nondet}{nondet}
\SetKwFunction{run}{run}
\SetKwFunction{learn}{learn}
\SetKwFunction{continue}{continue}
\SetKwFunction{assign}{assign}
\SetKwRepeat{Do}{do}{while}
%\SetKwFunction{assume}{assume}
%\SetKwFunction{isf}{isFeasible}
\SetKwData{safe}{safe}
\SetKwData{unsafe}{unsafe}
\SetKwData{true}{true}
\SetKwData{false}{false}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\SetKw{KwNot}{not}
\begin{small}
\Input{A counterexample trace $t$ of Program $P$}
\Output{The status (\true) if $t$ is not spurious and $t$ is complete 
or (\false) if $t$ is spurious or not complete}
\uIf{loopselect $\in$ t} {
   \uIf{loopselect==false} {
      \uIf{gamma\_complete(t)} {
        return \true \;
      }
      \uElse 
      {
        return \false \;
      }
   }
   \uElse {
     return \false \;
   }
}
\end{small}
\caption{Spurious Counterexample Checking \label{Alg:spurious-check}}
\end{algorithm2e}

\begin{algorithm2e}[t]
\DontPrintSemicolon
\SetKwFunction{decide}{Decide}
\SetKwFunction{deduce}{deduce}
\SetKwFunction{backtrack}{backtrack}
\SetKwFunction{print}{print}
\SetKwFunction{return}{return}
\SetKwFunction{nondet}{nondet}
\SetKwFunction{run}{run}
\SetKwFunction{learn}{learn}
\SetKwFunction{continue}{continue}
\SetKwFunction{assign}{assign}
\SetKwRepeat{Do}{do}{while}
\SetKwData{safe}{safe}
\SetKwData{unsafe}{unsafe}
\SetKwData{true}{true}
\SetKwData{false}{false}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\SetKw{KwNot}{not}
\begin{small}
\Input{A counterexample trace $t$ of Program $P$}
\Output{The status (\true) if $t$ is complete, else \false if $t$ is not complete} 
\For{elements $e \in t$} {
  \uIf{$e$ is non-singleton} {
    return \false \;  
  }
}
return \true \;  
\end{small}
\caption{Gamma Completeness Check \label{Alg:gamma-complete}}
\end{algorithm2e}
